Make any stupid plot you want

### 2021-02-12 draft/sections/intro.tex
I can has todo list

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
In data visualization it is assumed the graphical representation of data match the properties of the data, and in this work we propose that the mathematical notion of equivariance formalizes this expectation. We propose a topological model that can encode heterogenous components of topologically complex datasets. To demonstrate the practical value of our model, we propose a model driven re-architecture of the artist layer of the Python visualization library Matplotlib. In addition to providing a way to ensure the library preserves structure, we propose a functional approach to  improve modularity, maintainability, and point to ways in which the library could better support concurrency and interactivity.

>>>>

\documentclass[../main.tex]{subfiles}
\begin{document}
\section{Introduction}
\label{sec:intro}
"We have a unified mathematical description of understanding visualization.  Lots of people have worked on this and each has identified and described important aspects, but each has specialized in some way and it is not clear how to align them.  We can understand all of the prior work via our framework that pulls from {established math}"
that way you make clear what your contribution is, gives you a context to bring up all of the citations, a frame to contrast them, and then a nice lead into the math
I like your framing
and "we validate the framework by using it to re-design artist and data access layer of Maptlotlib, a general purpose visualization tool"

In data visualization it is assumed the graphical representation of data match the properties of the data, and in this work we propose that the mathematical notion of equivariance formalizes this expectation. We propose a topological model that can encode heterogenous components of topologically complex datasets. To demonstrate the practical value of our model, we propose a model driven re-architecture of the artist layer of the Python visualization library Matplotlib. In addition to providing a way to ensure the library preserves structure, we propose a functional approach to  improve modularity, maintainability, and point to ways in which the library could better support concurrency and interactivity.

### 2021-02-12 draft/sections/next.tex
I can has todo list

\begin{document}

%% proposed work:
%% transition functions, how it'd work on bundles
%% compositing + algebra
%% interactivity
%% implementation

>>>>

\begin{document}
\section{Discussion}

\subsection{What are the limitations?}
Is not useful for much yet.

\subsection{What else needs to be implemented?}
\begin{itemize}
    \item heatmaps/ proof of concept of face simplex
    \item composition algebra
    \item boxplot - multiglyph composition
    \item debatable: non-trivial bundle like data on mobius backend
    \item interactivity 
    \item concurrent artist
    \item numpy wrapper
\end{itemize}
\begin{itemize}
    \item provisional implementation using new architecture in Matplotlib
    \item developer-aimed documentation (API + narrative)
    \item proof of concept 3rd party user-facing library with a biology partner
    \item academic paper about building visualization tools on top of the core architecture
\end{itemize}

\subsection{What are the lessons learned?}

### 2021-02-12 draft/sections/scraps.tex
I can has todo list

\begin{figure}[ht!]
    \includegraphics[width=\textwidth]{figures/math/rotation_actions.png}
    \label{fig:data_monoid_rotation}
    \caption{The set of rotation actions [turn 0, 90, 180] on the star produce a star (closed), include a rotation that does not change the orientation (identity), and can be done in any order to produce the same final orientation (closure); therefore the rotations are a set of monoid actions.
    %% dataset that is symmetric, fiber is x,y, rotatation action
    %% rotate + plot or plot + rotate
    %%emoji shuffle 
    }  
\end{figure}

\begin{figure}[ht!]
    \includegraphics[width=.5\linewidth]{figures/math/fiberbundle.png}

    \caption{ The fiber $F$ is a continuous plane encoding the set of all possible (time, temperature) values.  The base space $K$ expresses that the fibers lie in continous space and therefore the data is continuous. The mapping $\pi:E\rightarrow K$ from total space to base space is what defines this structure as a fiber bundle. The continuous function $\tau_1$ returns a record in each fiber for each point on $K$; the set of all values $\tau_1$ returns is a dataset that lies in this fiberbundle. \note{remove one of the sections from this figure/maybe kill this example}}
    \label{fig:data_base_space} 
\end{figure}
The fiber bundle in figure~\ref{fig:data_base_space} is a representation of continuous (temperature, time) data. The fiber bundle abstraction facilitates seperately representing the time and temperature variables in the fiber $F$ and how these variables are connected in the base space $K$.  The function $\tau_1$ returns a record (temperature, time) for ever point on the interval $K$ and there can be many $\tau$ functions in the fiber bundle.

>>>>

s demonstrate that this framework of artists (functor between sheafs) works for all or possibly almost all the pyplot module as a composition of primitive artists of this framework. It's kind of like your table but we will need to walk through Q carefully and look at how sampling will function in quiver plots,
and contour plots. You will absolutely not have to have this worked out for the proposal, I'm just saying, composition, and demonstration of feasibility for the rest of pyplot will be important.
You will have the code for many/some of the primitives (eg scatter, line, bar, imshow, spine), and a description of the composition operator (which is a union/join/+). You will also need to realize K as a triangulated space (possibly CW-Complex) for the purposes of the computation.

The fun part for you can go through the ideas in Munsner, Bertin, Heer, Wilkonson interpreting these things in terms of the prior work. That sounds to me like a bookchapter. We will have to see if there is an opertunity to get that sent somewhere. You won't have much time for this for you proposal but if we have published a coherent model, this could be a nice desert.

Other things that may or may not play a big role would be working out the details of the S->K interaction for dashboards. By this I particularly mean when S is a composite object spanning all the figures shown in the dashboard and a component of K may have different compoents of S mapping into it slicing it in different ways.

*********************
One thought I had that might be a blocker we hit several times, and we already discussed this, is the difference between the object, and how it is represented. The number 6 is called "perfect" because it is the sum of its proper divisors 1,2, and 3. If we wrote 6 in binary, 110, it would still be the sum of its proper divisors, 1, 10, 11. "6" as a postive number is independent of how you represent it in binary, hex, octal or whatever. The fact 111 has 3 digits which are "1" is no a property of the number unless you add in the representation in base 10. In may (and physics and other sciences) we are constantly keeping track of what things are artifacts of our implementation, and what is invariant to ANY implementation. In CS I often run into students getting this confused. If you don't implement in a very particular way, constrained by the math, you end up breaking the invariance.
